---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Carbon stocks assessment with National Forest Inventories Data
###### Loading the required Packages---------
```{r, message=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(stringr)
library(maps)
library(mapdata)
library(maptools)
library(sp)
library(raster)
library(BIOMASS)
library(ape)
library(magrittr)
```

######load the dataframe 
```{r}
Trees <- read.csv("Data/MainFrame.csv")
```

###### Omitting the EAST and NORT with NA values and taxonomy of trees are corrected by using the to correct typos in scientific names using the Taxonomic Name Resolution Service 

```{r, message=FALSE}
Trees <- Trees[!is.na(Trees$NORTH),]
sum(is.na(Trees$EAST))

dim(Trees)
TreesNA <- Trees[Trees$Species=="NA",]
Trees <- Trees[!is.na(Trees$Species),]
dim(Trees)
summary(Trees)
sum(!is.na(Trees))
Trees <- drop_na(Trees)
dim(Trees)
Taxo <- correctTaxo(genus= Trees$Genus, species = Trees$Species)

Trees$genusCorr <- Taxo$genusCorrected
Trees$speciesCorr <- Taxo$speciesCorrected

APG <- getTaxonomy(Trees$genusCorr, findOrder =T)

Trees$familyAPG <- APG$family

Trees$orderAPG <- APG$order
dataWD <- getWoodDensity(genus=Trees$genusCorr,
                         species=Trees$speciesCorr,
                         stand=NULL, family = Trees$familyAPG, region = "World")

Trees <- Trees %>% mutate(DBH_cm=DBH_mm/10) %>% mutate(WD=dataWD$meanWD)
```

###### Obtaining wood density
Obtaining Wood density - getWoodDensity assigns to each taxon a species- or genus-level average if at least one wood density value in the same genus as the focal taxon is available in the reference database. For unidentified trees or if the genus is missing in the reference database, the stand-level mean wood density is assigned to the tree (based on trees for which a value was attributed). 

###### Building a Diameter Height Model based on the first year data----------
```{r}
library(lme4)
Forests <- read.csv("Data/All_data_Final.csv")
ModelForHeight <- lmer(log(H_m)~log(Dbh_cm)+(1|Plot_id), REML = FALSE, data = Forests)
```
```{r}
ModelForHeight
```

newdata = expand.grid(Dbh_cm = 0:100, Plot_id = unique(Forests$Plot_id))
newdata$H_pred<-predict(ModelForHeight, newdata)
summary(ModelForHeight)
ranef(ModelForHeight)


HDmodels <- modelHD(D=Forests$Dbh_cm,
                    H = Forests$H_m,
                    drawGraph=TRUE,
                    useWeight=TRUE)
HDmodels

Best_HDmodel<- modelHD(D=Forests$Dbh_cm,
                       H=Forests$H_m,
                       method="log1",
                       useWeight =TRUE)



### Getting tree Height based on the best model -----------------------------------------------------------------------------

dataHlocal <-retrieveH(Trees$DBH_mm, Best_HDmodel)

Trees$H_m <- dataHlocal$H
Trees$WD_gcm3 <-  dataWD$meanWD

# Omitting trees having DBH less than 5cm-----
Trees <- Trees %>% filter(DBH_cm >= 5)

# Calculating the biomass of each tree----
# Where, D = Tree diameter (in cm), either a vector or a single value
# Wood density (in g/cm3), either a vector or a single value.
# Tree height (H in m), either a vector or a single value.
CoordsH <- cbind(Trees$EAST, Trees$NORTH)
Trees <- Trees %>% mutate(AGB=computeAGB(DBH_cm, WD_gcm3, H = H_m, coord = CoordsH, Dlim = NULL))
names(Trees)

Trees <- Trees %>% mutate(Carbon_Mg= AGB*0.471)
class(Trees)

head(Trees)
str(Trees)
Trees$genusCorr <- as.character(Trees$genusCorr)

write.csv(Trees, file = "Data/Trees_data.csv")



# Carbon_ha (assumed 1ha sample plots)--------
Trees <- read.csv("Data/Trees_data.csv")
Plot_carbon <- Trees %>% group_by(Plot_names,Year) %>% summarise(Carbon_ha = sum(Carbon_Mg))
summary(Plot_carbon$Carbon_ha)
class(Plot_carbon$Carbon_ha)
attach(Plot_carbon)
hist(Plot_carbon)

hist(Trees$DBH_cm, breaks = 50)
hist(Trees$H_m, breaks = 10)
plot(Trees$DBH_cm, Trees$H_m)


# Carbon_ha (1 ha sample plot) with different nested sampling method------

# Splitting the dataframe for large 50 m* 50m and medium plots 25m*25m-----------------------------------------------------------------------------------------

Trees_data <- read.csv("Data/Trees_data.csv")

head(Trees_data)
str(Trees_data)
Trees_1ha <- Trees_data %>% filter(DBH_mm >= 200)
Trees_50m <- Trees_data %>% filter(DBH_mm < 200)

# Calculating the carbon per ha for the large plots------
Plot_1ha <- Trees_1ha %>%
  group_by(Plot_names, Year, District,EAST,NORTH, Zone) %>%
  dplyr::summarise(C_Tree_total = sum(Carbon_Mg)) %>%
  mutate(C_ha=C_Tree_total)

# Calculating the carbon per ha for the medium plots----------
Plot_50M_Cha <- Trees_50m %>%
  group_by(Plot_names, Year, District, EAST, NORTH, Zone) %>%
  dplyr::summarise(C_Tree_total = sum(Carbon_Mg)) %>%
  mutate(C_ha=C_Tree_total/0.25)

# Combining dataframes of different plot size into one by replacing the NAs values with 0 so as to combine-----

Plot_Cha <- full_join(Plot_1ha_Cha,Plot_50M_Cha, by= "Plot_names")

Plot_Cha$Plot_names <- as.character(Plot_Cha$Plot_names)
Plot_Cha$District.x <- as.character(Plot_Cha$District.x)
Plot_Cha$District.y <- as.character(Plot_Cha$District.y)

is.na(Plot_Cha)
str(Plot_Cha)
Plot_Cha[is.na(Plot_Cha)] <- 0

# As total trees number is for 1 ha plot.
# to get the mean carbon per ha
Plot_Cha <- Plot_Cha %>% mutate(Total_C_ha = C_ha.x+C_ha.y)

hist(Plot_Cha$Total_C_ha, breaks=100)

# upper 1% of the data was omitted due to uncertainities associated-----

Cut_Out <- Plot_Cha %>%
  filter(Total_C_ha <= 625.2924) 


# Filling out missing Districts, Years, NORTH and EAST-----

names(Cut_Out)
str(Cut_Out)

x <- which(Cut_Out$District.x==0)
Cut_Out$District.x[x]<- Cut_Out$District.y[x]

y <- which(Cut_Out$District.y==0)
Cut_Out$District.y[y] <- Cut_Out$District.x[y]


Missing_Year_X <- which(Cut_Out$Year.x==0)
Cut_Out$Year.x[Missing_Year_X] <- Cut_Out$Year.y[Missing_Year_X]

Missing_Year_Y <- which(Cut_Out$Year.y==0)
Cut_Out$Year.y[Missing_Year_Y] <- Cut_Out$Year.x[Missing_Year_Y]


y <- which(Cut_Out$District.y==0)
Cut_Out$District.y[y] <- Cut_Out$District.x[y]


Missing_EAST_X <- which(Cut_Out$EAST.x==0)
Cut_Out$EAST.x[Missing_EAST_X] <- Cut_Out$EAST.y[Missing_EAST_X]

Missing_EAST_Y <- which(Cut_Out$EAST.y==0)
Cut_Out$EAST.y[Missing_EAST_Y] <- Cut_Out$EAST.x[Missing_EAST_Y]


Missing_NORTH_X <- which(Cut_Out$NORTH.x==0)
Cut_Out$NORTH.x[Missing_NORTH_X] <- Cut_Out$NORTH.y[Missing_NORTH_X]

Missing_NORTH_Y <- which(Cut_Out$NORTH.y==0)
Cut_Out$NORTH.y[Missing_NORTH_Y] <- Cut_Out$NORTH.x[Missing_NORTH_Y]



Missing_Zone_X <- which(Cut_Out$Zone.x==0)
Cut_Out$Zone.x[Missing_Zone_X] <- Cut_Out$Zone.y[Missing_Zone_X]

Missing_Zone_Y <- which(Cut_Out$Zone.y==0)
Cut_Out$Zone.y[Missing_Zone_Y] <- Cut_Out$Zone.x[Missing_Zone_Y]


PYAY <- which(Cut_Out$District.x == "PYAY")
Cut_Out$District.x[PYAY] <- "Pyay"

PYAY2 <- which(Cut_Out$District.y == "PYAY")
Cut_Out$District.y[PYAY2] <- "Pyay"

names(Cut_Out)

# Producing a clean dataframe----
Cleaned_Dataframe <- Cut_Out %>% dplyr::select(Plot_names, Year.x, District.x, Total_C_ha, EAST.x, NORTH.x, Zone.x)


Cleaned_Dataframe <- Cleaned_Dataframe %>% rename(Year = Year.x) %>% rename(District = District.x) %>% 
  rename(EAST = EAST.x) %>% rename(NORTH = NORTH.x) %>% 
  rename(Zone = Zone.x)

which(Cleaned_Dataframe$EAST==512000)
Wrong_Plot <- Cleaned_Dataframe %>% filter(Plot_names=="N512000E2077000")

Cleaned_Dataframe[7289, 5] = 215000

write.csv(Cleaned_Dataframe,file = "Data_Output/Cleaned_Data.csv",row.names = FALSE)

Final_Dataframe <- read.csv("Data_Output/Cleaned_Data.csv")

# Loading the NDVI data for 7 years----
NDVI2018_values <- read.csv("Data_Output/NDVI2018.csv")
NDVI2017_values <- read.csv("Data_Output/NDVI2017.csv")
NDVI2016_values <- read.csv("Data_Output/NDVI2016.csv")
NDVI2015_values <- read.csv("Data_Output/NDVI2015.csv")
NDVI2014_values <- read.csv("Data_Output/NDVI2014.csv")
NDVI2013_values <- read.csv("Data_Output/NDVI2013.csv")
NDVI2012_values <- read.csv("Data_Output/NDVI2012.csv")
NDVI2011_values <- read.csv("Data_Output/NDVI2011.csv")
NDVI2010_N_values <- read.csv("Data_Output/NDVI2010.csv")


# Attached NDVI values to the Data Frame----
Final_Dataframe <- read.csv("Data_Output/Cleaned_Data.csv")
Final_Dataframe$NDVI2018 <- NDVI2018_values$NDVI
Final_Dataframe$NDVI2017 <- NDVI2017_values$NDVI2017
Final_Dataframe$NDVI2016 <- NDVI2016_values$NDVI2016
Final_Dataframe$NDVI2015 <- NDVI2015_values$NDVI2015
Final_Dataframe$NDVI2014 <- NDVI2014_values$NDVI2014
Final_Dataframe$NDVI2013 <- NDVI2013_values$NDVI2013
Final_Dataframe$NDVI2012 <- NDVI2012_values$NDVI2012
Final_Dataframe$NDVI2011 <- NDVI2011_values$NDVI2011
Final_Dataframe$NDVI2010 <- NDVI2010_values$NDVI2010
Final_Dataframe <- Final_Dataframe

#  Histrograms of NDVI and Carbon for 7 years------

hist(Final_Dataframe$Total_C_ha, breaks = 100)
hist(Final_Dataframe$NDVI2018, breaks = 100)
hist(Final_Dataframe$NDVI2017, breaks = 100)
hist(Final_Dataframe$NDVI2016, breaks = 100)
hist(Final_Dataframe$NDVI2015, breaks = 100)
hist(Final_Dataframe$NDVI2014, breaks = 100)
hist(Final_Dataframe$NDVI2013, breaks = 100)
hist(Final_Dataframe$NDVI2012, breaks = 100)
hist(Final_Dataframe$NDVI2011, breaks = 100)
hist(Final_Dataframe$NDVI2010, breaks = 100)

# NFI Carbon data and NDVI relationship-----

# Year2017---------------
NFI_2017 <- Final_Dataframe %>% filter(Year==2017)
plot(NFI_2017$Total_C_ha, (NFI_2017$NDVI2017)/10000)

#  Year 2016---------
NFI_2016 <- Final_Dataframe %>% filter(Year==2016)
plot(NFI_2016$Total_C_ha, (NFI_2016$NDVI2016)/10000)

#  Year 2015----
NFI_2015 <- Final_Dataframe %>% filter(Year==2015)
plot(NFI_2016$Total_C_ha, (NFI_2016$NDVI2015)/10000)

#  Year 2014----
NFI_2014 <- Final_Dataframe %>% filter(Year==2014)
plot(NFI_2014$Total_C_ha, (NFI_2014$NDVI2014)/10000)


#  Year 2013----
NFI_2013 <- Final_Dataframe %>% filter(Year==2013)
plot(NFI_2013$Total_C_ha, (NFI_2013$NDVI2013)/10000)


#  Year 2012----
NFI_2012 <- Final_Dataframe %>% filter(Year==2012)
plot(NFI_2012$Total_C_ha, (NFI_2012$NDVI2012)/10000)


#  Year 2011----
NFI_2011 <- Final_Dataframe %>% filter(Year==2011)
plot(NFI_2011$Total_C_ha, (NFI_2011$NDVI2011)/10000)

#  Year 2010----
NFI_2010 <- Final_Dataframe %>% filter(Year==2010)
plot(NFI_2010$Total_C_ha, (NFI_2010$NDVI2010)/10000)

# 7 Year NFI carbon and NDVI----
plot(Final_Dataframe$Total_C_ha,Final_Dataframe$NDVI2018)
plot(Final_Dataframe$Total_C_ha,Final_Dataframe$NDVI2017)
plot(Final_Dataframe$Total_C_ha,Final_Dataframe$NDVI2016)
plot(Final_Dataframe$Total_C_ha,Final_Dataframe$NDVI2015)
plot(Final_Dataframe$Total_C_ha,Final_Dataframe$NDVI2014)
plot(Final_Dataframe$Total_C_ha,Final_Dataframe$NDVI2013)
plot(Final_Dataframe$Total_C_ha,Final_Dataframe$NDVI2012)
plot(Final_Dataframe$Total_C_ha,Final_Dataframe$NDVI2011)
plot(Final_Dataframe$Total_C_ha,Final_Dataframe$NDVI2010)

Final_Dataframe$NDVI_cyr<-NA
Final_Dataframe$NDVI_cyr[Final_Dataframe$Year==2010]<-Final_Dataframe$NDVI2010[Final_Dataframe$Year==2010]
Final_Dataframe$NDVI_cyr[Final_Dataframe$Year==2011]<-Final_Dataframe$NDVI2011[Final_Dataframe$Year==2011]
Final_Dataframe$NDVI_cyr[Final_Dataframe$Year==2012]<-Final_Dataframe$NDVI2012[Final_Dataframe$Year==2012]
Final_Dataframe$NDVI_cyr[Final_Dataframe$Year==2013]<-Final_Dataframe$NDVI2013[Final_Dataframe$Year==2013]
Final_Dataframe$NDVI_cyr[Final_Dataframe$Year==2014]<-Final_Dataframe$NDVI2014[Final_Dataframe$Year==2014]
Final_Dataframe$NDVI_cyr[Final_Dataframe$Year==2015]<-Final_Dataframe$NDVI2015[Final_Dataframe$Year==2015]
Final_Dataframe$NDVI_cyr[Final_Dataframe$Year==2016]<-Final_Dataframe$NDVI2016[Final_Dataframe$Year==2016]
Final_Dataframe$NDVI_cyr[Final_Dataframe$Year==2017]<-Final_Dataframe$NDVI2017[Final_Dataframe$Year==2017]
Final_Dataframe$NDVI_cyr[Final_Dataframe$Year==2018]<-Final_Dataframe$NDVI2018[Final_Dataframe$Year==2018]

Final_Dataframe %>%
ggplot(aes(x = log(Total_C_ha), y = NDVI_cyr, color = Year)) +
  geom_point() +
  geom_smooth(method = 'lm')


lm1 <- lm(log(Total_C_ha)~NDVI_cyr,data = Final_Dataframe)
summary(lm1)

# 2 Year Avitabile and NDVI as Avitabile used 2011 and 2012 AGB maps to produce his map-----------------------------------
Data_AVT <- read.csv("Data/AGB_AVT_plots.csv")
Data_AVT <- Data_AVT %>% mutate(AVT_Carbon= 0.47*(Data_AVT$mean))
Data_AVT$NDVI2012 <- NDVI2012_values$NDVI2012
Data_AVT$NDVI2011 <- NDVI2011_values$NDVI2011

Data_AVT <- Data_AVT
plot(Data_AVT$Total_C_ha, Data_AVT$AVT_Carbon)

#  Year 2012----
AVT_2012 <- Data_AVT %>% filter(Year==2012)
plot(AVT_2012$AVT_Carbon, (AVT_2012$NDVI2012)/10000)


#  Year 2011----
AVT_2011 <- Data_AVT %>% filter(Year==2011)
plot(AVT_2011$AVT_Carbon, (AVT_2011$NDVI2011)/10000)


# 2 Year AVT carbon and NDVI----

plot(Data_AVT$AVT_Carbon,Data_AVT$NDVI2012)
plot(Data_AVT$AVT_Carbon,Data_AVT$NDVI2011)

Data_AVT$NDVI_cyr<-NA
Data_AVT$NDVI_cyr[Data_AVT$Year==2011]<-Data_AVT$NDVI2011[Data_AVT$Year==2011]
Data_AVT$NDVI_cyr[Data_AVT$Year==2012]<-Data_AVT$NDVI2012[Data_AVT$Year==2012]

Data_AVT %>%
  ggplot(aes(x = log(AVT_Carbon), y = NDVI_cyr, color = Year)) +
  geom_point() +
  geom_smooth(method = 'lm')

lm1 <- lm(log(AVT_Carbon)~NDVI_cyr,data = Data_AVT)
summary(lm1)



# summary observations..
unique(Final_Dataframe$District)
table(Final_Dataframe$District)
table(Final_Dataframe$Year)


PlotNumber_by_District <- Final_Dataframe %>%
  group_by(District) %>%
  summarise(count = n())

# Load up the values extracted from the AVitabile AGB Map----
  
Data_AVT <- read.csv("Data/AGB_AVT_plots.csv")
Data_AVT <- Data_AVT %>% mutate(AVT_Carbon= 0.47*(Data_AVT$mean))

# calculating the Average ABG value for each district for Aviatabile and NFI
Data_AVT_Dist <- Data_AVT %>% group_by(District) %>% summarise(mean_C_AVT = mean(AVT_Carbon, na.rm = T, n= n()))

mean_DistC_Total <-  Data_AVT %>% group_by(District) %>% summarise(mean_C_Total = mean(Total_C_ha, na.rm = T, n= n()))

Data_AVT_Dist$Mean_C_Field <- mean_DistC_Total$mean_C_Total

# Writing the csv file of Avitabile avearage carbon for each district

write.csv(Data_AVT_Dist, file = "Data_Output/CarbonDistrictL.csv", row.names = FALSE)

CarbonDistrictL <- read.csv("Data_Output/CarbonDistrictL.csv")

plot(CarbonDistrictL$mean_C_AVT, CarbonDistrictL$Mean_C_Field,col= "red", main= "Correlation between Avitabile Map Data and NFI Data") %>% abline()

CarbonDistrictL %>% ggplot(aes(x = District , y = mean_C_AVT, fill = District)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  labs(
    x = "District",
    y = "Average Carbon Storage (Mg)",
    title = paste(
      "Average Carbon Storage by Avitabile Map"
    )
  )+theme(axis.text.x = element_text(size=9, angle=90, vjust=0.5), 
          axis.text.y = element_text(size=9))


CarbonDistrictL %>% ggplot(aes(x = District , y = Mean_C_Field, fill = District)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  labs(
    x = "District",
    y = "Average Carbon Storage (Mg)",
    title = paste(
      "Average Carbon Storage by NFI"
    )
  )+theme(axis.text.x = element_text(size=9, angle=90, vjust=0.5), 
          axis.text.y = element_text(size=9))



ggplot(data = CarbonDistrictL, aes(x=mean_C_AVT, y=Mean_C_Field))+ geom_point(aes(colour = District))+ labs(xlab="Avitabile(ton/ha)", ylab = "NFI_Carbon(ton/ha)", title = "NFI carbon and Avitabile Carbon Relationship")

# Testing based on the training lessons
Test_Data <- read.csv("data/distance_to_cities.csv")
EX2Plot <- Test_Data %>%  filter(year==2011) %>% ggplot(mapping = aes(x=Total_C_ha, y=mean))+ geom_point(color="red")+ geom_smooth(color= "green")+theme_bw()

Survey_2012 <- Test_Data %>% select(Year, Total_C_ha, mean, District) %>% 
  filter(Year == 2012)

ggplot(Survey_2012, aes(x= Total_C_ha, y = mean))+ geom_point()+theme_bw()


ggplot(data = Test_Data, aes(x=Total_C_ha, y=mean))+ geom_point(aes(colour = District))+ geom_density_2d(data = Survey_2012, colour= "navyblue")





## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


