---
title: "Fieldwork Analysis"
author: "ONEILL"
date: "10/11/2019"
output: html_document
---


```{r}
library(tidyverse)
library(lubridate)
library(BIOMASS)
library(ape)
library(ggplot2)

```

```{r}
Field_Data <- read.csv("Data/Popa_Fieldwork/Popa_Fieldwork(23-10-2019).csv", stringsAsFactors = F)
```

**Checking typos in taxonomy**

```{r}
Taxo <- correctTaxo(genus=Field_Data$Genus, species = Field_Data$Species)
Field_Data$genusCorr <- Taxo$genusCorrected
Field_Data$speciesCorr <- Taxo$speciesCorrected
```
**Retrieving APG III Families and Orders from Genus names**

```{r}
APG <- getTaxonomy(Field_Data$genusCorr, findOrder = T)
Field_Data$familyAPG <- APG$family
Field_Data$orderAPG <- APG$order
```

**RETRIEVE WOOD DENSITY**

```{r}
dataWD <- getWoodDensity(genus=as.character(Field_Data$genusCorr),
                         species=as.character(Field_Data$speciesCorr),
                         stand=Field_Data$Plot)
```


```{r}
sum(dataWD$levelWD == "species")

sum(dataWD$levelWD == "genus")

sum(!dataWD$levelWD%in%c("genus","species"))

Field_Data$WD <- dataWD$meanWD
str(Field_Data)




```

**Computing AGB**

```{r}
AGBtree<-computeAGB(D=Field_Data$DBH_cm,
                    WD=Field_Data$WD,
                    H = Field_Data$Height_m)
# Compute AGB(Mg) per tree----
Field_Data$AGB_Mg <- AGBtree

# Compute Carbon (Mg) per tree --
Field_Data <- Field_Data %>%
  mutate(Carbon_Mg= AGB_Mg*0.47) %>% mutate(C_Tree_Ha = Carbon_Mg/0.04)
str(Field_Data)
Field_Data$Plot <- factor(Field_Data$Plot)

boxplot(C_Tree_Ha~Plot, data=Field_Data)
summary(aov(C_Tree_Ha ~ factor(Plot), data = Field_Data))
 
Field_Carbon <- Field_Data %>%
  group_by(Plot) %>%
  dplyr::summarise(Total_C = sum(C_Tree_Ha), Elevation = mean(Elevation_m)) %>% rename(Plot_Number=Plot)

ggplot(data=Field_Carbon, aes(x=as.numeric(Plot_Number),y =Total_C, color=as.numeric(Plot_Number)))+ geom_point()+ geom_line()+
      labs(title = "Carbon storage in 20 Permanent sample plots", 
       x= "Plot",
       y= "Carbon(t/ha)")+
  theme(axis.text.x = element_text(size=7, angle = 0, vjust = 0.5),
        axis.text.y = element_text(size = 7))

write.csv(Field_Carbon, file = "Data_Output/Field_Carbon.csv", row.names = F)
 

```

```{r}
hist(Field_Data$Height_m)
hist(Field_Data$DBH_cm)
ggplot(data = Field_Data, aes(y = Height_m, x = log(DBH_cm))) + 
  geom_point(color='green') +
  geom_smooth(method = "lm", se = FALSE)

```
**convert from decimal minutes to decimal degrees**

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(stringr)
library(maps)
library(mapdata)
library(maptools)
library(sp)
library(raster)
library(BIOMASS)
library(ape)
library(magrittr)
library(tinytex)
library(raster)
library(rgdal)
library(measurements)

# Field_Data <- read.csv("Data/Popa_Fieldwork/Popa_Fieldwork(23-10-2019).csv", stringsAsFactors = F)
# head(Field_Data)
# sum(is.na(Field_Data$North))
# sum(is.na(Field_Data$East))
# str(Field_Data)
# 
# Field_Data$North = gsub('  ', ' ',Field_Data$North)
# Field_Data$East = gsub('  ', ' ',Field_Data$East)
# 
# Field_Data$Lat = conv_unit(Field_Data$North, from = 'deg_min_sec', to = 'dec_deg')
# Field_Data$Long = conv_unit(Field_Data$East, from = 'deg_min_sec', to = 'dec_deg')
# 
# write.csv(Field_Data, file="Data_Output/FieldPlots.csv", row.names = F)



Field_Data <- read.csv("Data_Output/FieldPlots.csv")
world2HiresMapEnv

data(wrld_simpl)
myanmar <- wrld_simpl[wrld_simpl$NAME=="Burma",]

FPopaPlots <- Field_Data %>% group_by(Plot) %>% summarise(Long= mean (Long),Lat=mean(Lat))
coords = cbind(FPopaPlots$Long, FPopaPlots$Lat)
llCRS <- CRS("+init=epsg:4326")
Coords_sp <- SpatialPoints(coords, proj4string = llCRS)
Coords_sp <- spTransform(Coords_sp, "+init=epsg:4326")

spdf = SpatialPointsDataFrame(Coords_sp,data = FPopaPlots)
writeOGR(spdf,"FieldPopa_plots.shp", layer="Coords_sp", driver = "ESRI Shapefile")
plot(myanmar)
plot(Coords_sp)

```
```{r}
EVI2018Popa <-raster("Data/EVI2018_Popa.tif")
mypts <-readOGR("Field_Plots_shapefile/FieldPopa_plots.shp")
EVI2018Popa <- trim(EVI2018Popa)
plot(EVI2018Popa)
mydata <- raster::extract(EVI2018Popa, mypts)
plot(mypts, add = TRUE, cex=0.1)

class(mydata)
EVI2018_values <- as.data.frame(mydata)
EVI2018 <- EVI2018_values %>% rename(EVI2018=mydata)
Plot_names <- read.csv("Data_Output/FieldPlots.csv",stringsAsFactors = F)
Plots_EVI2018 <- Plot_names %>% group_by(Plot) %>% summarise(Long = mean(Long),Lat=mean(Lat))
EVI2018_Popa <- bind_cols(Plots_EVI2018,EVI2018)
EVI2018_Popa <- EVI2018_Popa %>% rename(Plot_Number=Plot)


```
Joining Field Carbon and EVI

```{r}
Field_Carbon <- read.csv("Data_Output/Field_Carbon.csv", stringsAsFactors = F)
EVI2018_Popa$Carbon <-  Field_Carbon$Total_C
EVI2018_Popa$Elevation <- Field_Carbon$Elevation
Carbon_EVI_Popa <- EVI2018_Popa
plot(Carbon_EVI_Popa$Carbon, Carbon_EVI_Popa$EVI2018)
plot(Carbon_EVI_Popa$Carbon, Carbon_EVI_Popa$Elevation)

write.csv(Carbon_EVI_Popa,file = "Data_Output/Carbon_EVI_Popa.csv", row.names = F)
```
**Carbon and environmental conditions relationship** 

BIO1 = Annual Mean Temperature  
BIO2 = Mean Diurnal Range (Mean of monthly (max temp - min temp))  
BIO3 = Isothermality (BIO2/BIO7) (* 100)  
BIO4 = Temperature Seasonality (standard deviation *100)  
BIO5 = Max Temperature of Warmest Month  
BIO6 = Min Temperature of Coldest Month  
BIO7 = Temperature Annual Range (BIO5-BIO6)  
BIO8 = Mean Temperature of Wettest Quarter  
BIO9 = Mean Temperature of Driest Quarter  
BIO10 = Mean Temperature of Warmest Quarter  
BIO11 = Mean Temperature of Coldest Quarter  
BIO12 = Annual Precipitation  
BIO13 = Precipitation of Wettest Month  
BIO14 = Precipitation of Driest Month  
BIO15 = Precipitation Seasonality (Coefficient of Variation)  
BIO16 = Precipitation of Wettest Quarter  
BIO17 = Precipitation of Driest Quarter  
BIO18 = Precipitation of Warmest Quarter  
BIO19 = Precipitation of Coldest Quarter  

I performed a simple liner regression analysis on the two variables Carbon and Annual precipitaion(AP)/Annual Mean Temperature(AMT). I wish to determine wheter the AP/AMT varible is a significant predictor of the Carbon Variable.

```{r}
Carbon_EVI_Popa <- read.csv("Data_Output/Carbon_EVI_Popa.csv", stringsAsFactors = F)
WCL_Popa <- read.csv("Data_Output/WCL_Popa.csv", stringsAsFactors = F) %>% rename(Plot_Number=Plot)
CEVI_WCL_Popa <- Carbon_EVI_Popa %>% inner_join(WCL_Popa, by = "Plot_Number",suffix = c(".EVI", ".WCL"), all = T) %>% rename(Long= Long.EVI, Lat=Lat.EVI) %>% dplyr::select(-c(Long.WCL, Lat.WCL))


plot(Carbon~bio01, data = CEVI_WCL_Popa)
glm.AMT <- glm(log(Carbon)~bio01,data=CEVI_WCL_Popa, family = gaussian(link = "identity"))
summary(glm.AMT)
plot(glm.AMT)

ggplot(data=CEVI_WCL_Popa, aes(x=bio01, y = Carbon, color=as.factor(Plot_Number)))+ geom_jitter()+
  labs(title = "Carbon storage and Annual Mean Temperature Relationship", 
       x= "Annual Mean Temperature(°C)",
       y= "Carbon(t/ha)")+
  theme(axis.text.x = element_text(size=7, angle = 45, vjust = 0.5),
        axis.text.y = element_text(size = 7))


plot(Carbon~bio12, data = CEVI_WCL_Popa)
glm.AMT <- glm(log(Carbon)~bio12,data=CEVI_WCL_Popa, family = gaussian(link = "identity"))
summary(glm.AMT)
plot(glm.AMT)

ggplot(data=CEVI_WCL_Popa, aes(x=bio12, y = Carbon, color=as.factor(Plot_Number)))+ geom_jitter()+
  labs(title = "Carbon storage and Annual Precipiation Relationship", 
       x= "Annual Precipiation (mm)",
       y= "Carbon(t/ha)")+
  theme(axis.text.x = element_text(size=7, angle = 45, vjust = 0.5),
        axis.text.y = element_text(size = 7))



write.csv(CEVI_WCL_Popa, file="Data_Output/Carbon_EVI_Popa.csv", row.names = F)

```
**Load up the values extracted from the AVitabile AGB Map**

```{r}
Avt_Carbon_Popa <- read.csv("Data_Output/Avitabile_AGB_Popa.csv", stringsAsFactors = F)
All_Plot_info <- read.csv("Data_Output/Carbon_EVI_Popa.csv", stringsAsFactors = F)
AVt_Fieldwork <- Avt_Carbon_Popa %>% inner_join(All_Plot_info, by = "Plot_Number",suffix = c(".Avt", ".FW"), all = T) %>% rename(Lat=Lat.FW, Long = Long.FW) %>% dplyr::select(-c(Lat.Avt, Long.Avt))

attach(AVt_Fieldwork)
plot(Carbon~Mean_Avt_Carbon, data = AVt_Fieldwork)
glm.Avt_FW <- glm(Carbon~Mean_Avt_Carbon,data = AVt_Fieldwork, family = gaussian(link = "identity"))
summary(glm.Avt_FW)
plot(glm.Avt_FW)

ggplot(data=AVt_Fieldwork, aes(x=Mean_Avt_Carbon, y = Carbon, color=as.factor(Plot_Number)))+ geom_jitter()+
  labs(title = "Fieldwork Carbon storage and Avitabile Carbon Relationship", 
       x=expression(bold(paste("Carbon predicted by Avitabile t ", ha^bold("-1")))),
       y= expression(bold(paste("Carbon calculated from fieldwork t ", ha^bold("-1")))))+
  theme(axis.text.x = element_text(size=7, angle = 45, vjust = 0.5),
        axis.text.y = element_text(size = 7))

```

**Loading Last Year's Popa datasets here to check with the field dataset I collected**

```{r}
First_Year_Forests <- read.csv("Data/All_data_Final.csv", stringsAsFactors = F)
Popa_Forests <- First_Year_Forests %>% filter(Forest_type!="Moist_Mixed_Deciduous_Forest") %>% filter(Forest_type!="Dry_Mixed_Deciduous_Forest")

NA_Rows <- Popa_Forests %>% filter(!complete.cases(.))

DF$col[is.na(DF$col)] <- "None"
NA_Rows$Species_names[is.na(NA_Rows$Species_names)] <- "Unknown species"
NA_Rows$Genus[is.na(NA_Rows$Genus)] <- "Unknown"
NA_Rows$Species[is.na(NA_Rows$Species)] <- "species"
NA_Rows$Family[is.na(NA_Rows$Family)] <- "Unknown"
NA_Rows_Completed <- NA_Rows

Complete_Rows <- Popa_Forests %>% filter(complete.cases(.))

Popa_Forests_Full <- rbind(Complete_Rows, NA_Rows_Completed)

```


names(Forests)
Forests <- filter(Forests,!is.na(Species_names) & !is.na(Dbh_cm))
summary(Forests)
unique(Forests$Forest_type)

LogDH_Selected_Forests <- Selected_Forests %>% mutate(LogDbh_cm=log(Dbh_cm)) %>% mutate(LogH_m=log(H_m))
ggplot(data = Selected_Forests, aes(Dbh_cm, H_m, color=Forest_type) )+ geom_point()
ModelForHeight <- lmer(log(H_m)~log(Dbh_cm)+(1|Plot_id), REML = FALSE, data = Selected_Forests)
ModelForHeight
ranef(ModelForHeight)$Plot_id[,1] %>% hist()

ModelForHeight_Log <- lmer(LogH_m~LogDbh_cm +(1|Plot_id), REML = FALSE, data = LogDH_Selected_Forests)
ModelForHeight_Log

